Modelos

### 2019-01-21 20190117_modelos.Rmd
SUNDAY01
SUNDAY02

```{r library, message=FALSE, warning=FALSE}
options(scipen=999)
library(haven)
library(dplyr)
library(car)
library(stargazer)
library(ggplot2)
library(gridExtra)
library(knitr)
library(kableExtra)
library(RItools) #xBalance
library(texreg)
library(lavaan)
library(sjPlot)

@@

table(tpad2$TIPO2)
table(tpbd2$TIPO2)
table(tpcd2$TIPO2)

>>>>

```{r library, message=FALSE, warning=FALSE}
options(scipen=999)
library(haven)
library(dplyr)
library(car) 
library(stargazer)
library(ggplot2)
library(gridExtra)
library(knitr)
library(kableExtra)
library(RItools) #xBalance1
library(texreg)
library(lavaan)
library(sjPlot)

@@

table(tpad2$TIPO2) #table
table(tpbd2$TIPO2)
table(tpcd2$TIPO2)
